Results discussion

### 2024-11-06 pages/results_discussion.qmd
docs(results discussion): adding some of tom's comments, and section with evidence for frmaework components

@@

"Reflections" in this group:

@@

Note: Data dictionaries are relevant to inputs and outputs.

@@

@@

@@

>>>>

(Addressing Tom's suggestion - "Maybe there are some high level groupings of your findings? e.g. Study reporting; Model structuring and functionality; Analysis pipeline")

@@

Notes:

* Tom: Key for STARS 2.0: seeds

@@

Notes:

* Data dictionaries are relevant to inputs and outputs.
* Some of these can become "less of an issue" for reproduction if there is a reproducible analytical pipeline, as don't need to delve into it and troubleshoot (but are still relevant for reuse).

@@

Many of these headlines link to the importance of reproducible analytical pipelines (RAP) for simulation.

@@

(Also addressing Tom's suggestion: "Evidence supporting the use of reporting guidelines... as in - reporting guidelines state this should info be included and you found it v.difficult or impossible to reproduce without it")

@@

## Evidence for framework components

Reflections:

* "Include instructions on how to run the model/script" --> Evidence for STARS essential component minimum documentation
* "For slow models, state the expected run time" --> Evidence for STRESS-DES 5.4
* "For computationally expensive models, state memory usage and provide alternatives for lower spec machines" --> Evidence for STRESS-DES
* "Provide all the required parameters" and "If not provided in the script, then *clearly* present all parameters in the paper" --> Evidence for STRESS-DES 3.3
